### 2014-10-31 Introduction.tex
stuff

\item A general \emph{modular verification methodology} applicable to hardware
  algorithms, based on \emph{labeled transition systems}.  We are able to verify
  the several components of Figure~\ref{zoom} \adam{OK to have a
    forward reference to this figure?} against general formal interfaces,
  enabling mixing and matching of different realizations of each interface,
  without doing any new proofs that peek beneath abstraction boundaries.

>>>>

\item A general \emph{modular verification methodology} applicable to hardware
  algorithms, based on \emph{labeled transition systems}.
We are able to verify
  the several components of a modern processor 
\adam{(Figure~\ref{zoom} OK to have a forward reference to this figure?}
against general formal interfaces,
  enabling mixing and matching of different realizations of each interface,
  without doing any new proofs that peek beneath abstraction boundaries.
